Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-28 manuscript.Rmd
Add page number for quote

The type of collective contentious behavior that manifests in society is a
function of the available political opportunity structures. The political
opportunity structure is “comprised of *(sic)* specific configurations of
resources, institutional arrangements and historical precedents for social
mobilization, which facilitate the development of protest movements in some
instances and constrain them in others” [@kitschelt1986political]. Emergent strategies and tactics in contentious politics are a function of
what the system makes possible. This includes the number of people and their
disposition (i.e. nonviolent or violent), as well as their internal structure.
The more cohesive a group is, the greater threat they pose to the establishment.

>>>>

The type of collective contentious behavior that manifests in society is a
function of the available political opportunity structures. The political
opportunity structure is “comprised of *(sic)* specific configurations of
resources, institutional arrangements and historical precedents for social
mobilization, which facilitate the development of protest movements in some
instances and constrain them in others” [@kitschelt1986political, p. 58]. Emergent strategies and tactics in contentious politics are a function of
what the system makes possible. This includes the number of people and their
disposition (i.e. nonviolent or violent), as well as their internal structure.
The more cohesive a group is, the greater threat they pose to the establishment.
